DATA 621 - Business Analytics and Data Mining

### 2020-10-27 HW3/HW3_Final_AA.Rmd
remove unneded libraries, add crtl_grid

```{r loadData, include=FALSE}
library(tidyverse)
library(tidymodels)
library(data.table)
library(stacks)
library(kernlab)
library(vip)
library(summarytools)
library(corrplot)
library(knitr)
library(rsample) # model 1 libraries
library(caret)
library(geoR)

@@

>>>>

```{r loadData, include=FALSE}
library(tidyverse)
library(tidymodels)
library(data.table)
library(vip)
library(summarytools)
library(corrplot)
library(knitr)
library(rsample) # model 1 libraries
library(caret)
library(geoR)

@@

crtl_grid<-control_grid(verbose = FALSE)
